---
title: "Python Environment Setup"
author: "B Steele"
date: "2022-12-27"
output: html_document
---

## Load packages, install miniconda, install python modules

This chunk gets you ready to have a reproducible workspace in your R Project directory. You'll only have to run this script once in order to set up the python environment. After this instance, you should be good-to-go. Installation of miniconda and the `py_install()` function here is for your system. You may get a notice that requirements are already satisfied, and that is okay.

```{r}
library('reticulate')
library('tidyverse')
try(install_miniconda())
py_install(c('h5py', 'numpy', 'scikit-image', 'gdal', 'pandas', 'matplotlib'))
```

Now, set up the virtual environment, activate it, and install needed python modules.

```{r}
#grab your current WD
dir = getwd()
#create a conda environment named 'imgproc' with the modules needed
conda_create(envname = file.path(dir, 'imgproc'),
             packages = c('h5py', 'numpy', 'scikit-image', 'gdal', 'pandas', 'matplotlib'))
Sys.setenv(RETICULATE_PYTHON = file.path(dir, 'imgproc/bin/python/'))
use_condaenv("imgproc/")
#print the configuration
py_config()
```

Now, install the python modules into your conda environment:

```{r}
py_install(packages = c('h5py', 'numpy', 'scikit-image', 'gdal', 'pandas', 'matplotlib'), envname = 'imgproc/')

```

That's all to this step!
